\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{bm}

% Ensure that generate pdf is machine readable/ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1
\DisableLigatures{encoding = *, family = *}

%----------FONT OPTIONS----------
\usepackage{sansmathfonts}
\renewcommand*\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

% Sectional formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\Large
}{}{0em}{}[\color{black} \titlerule{} \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item \small {
        {#1 \vspace{-3pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{#2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, label={\textbullet}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Shubham Nitin Joshi} \\
    \href{mailto:shubham.joshi1507@gmail.com}{\underline{snj150731@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/shubham-j-993785120/}{\underline{linkedin.com/in/shubham-j-993785120}} $|$
    \href{https://github.com/shubham1507}{\underline{github.com/shubham1507}} $|$
    \href{tel:8390246938}{\underline{Phone: 7276782952}}
\end{center}

\vspace{-15pt}

%----------- PROFILE -----------
\section{Profile}
\small{
    Senior Software Engineer with 7 years of experience, including 3 years in full-stack development and 4 years specializing in DevOps. \\
    Proficient in tools and technologies like Jenkins, Azure DevOps, GCP, Terraform, Ansible, Docker, and Kubernetes. Focused on advancing expertise in the DevOps domain. \\
}

\vspace{-15pt}

%----------- SKILLS -----------
\section{Skills}
\begin{itemize}[leftmargin=0.25in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript, Bash Shell, Go} \\
     \textbf{Libraries/Frameworks}{: Django, Django REST Framework, Angular} \\
     \textbf{IaC}{: Terraform, Ansible} \\
     \textbf{Cloud \& DevOps}{: Microsoft Azure/AWS/GCP, GitHub, Jenkins, Docker, Kubernetes} \\
     \textbf{Tools \& Databases}{: Git, Octopus Release, Linux (Ubuntu), PostgreSQL, Jira, JFrog Artifactory, Nexus, sonarqube} \\
     \textbf{Monitoring tool}{: opentelemtry, AppDynamics} \\
     \textbf{Platform engineering tool}{: Backstage IDP } \\
    }}\\
\end{itemize}

\vspace{-25pt}

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
\resumeSubHeadingListStart{}
    \resumeSubheading{TEK Systems, Pune}{25 Nov 2024 \textendash{} Present}
        {Senior Software Engineer}{Hybrid}
        \resumeItemListStart{}
            \item[] \textbf{Project 1:HSBC - WSIT Caching As a Service}
            \begin{itemize}[leftmargin=0.5in, label={\textbullet}]
                \item As a SRE automation Engineer designed and developed pipeline using Jenkins and declarative \textbf groovy scripting.
                \item Created modular ansible playbook to interact with pipeline to automate SRE activities,deployments and monitoring on 
                hazelcast plaform(a caching platform like redies).
                \item Used bash shell scripting and python for server configurations like node/management center upgradation.
                \item For monitoring and alerting configured hazelcast eco-system with \textbf opentelemtry with AppDynamics.
                \item Configured and implemented modular services using terraform for infrastructure as code.
                \item Maintained production/non-production ansible templates with \textbf Ansible tower.
                \item To reduce Jenkins-interaction with developers and stakeholders created YAML based templates and custom-plugins
                 using \textbf backstage IDP (platform tool).
                \item Contributed as individual for \textbf TPAM(PAR) reduction activities for SRE's using automation over hazelcast platform.
                
                
            \end{itemize}
        \resumeItemListEnd{}
        
    \vspace{10pt} % Space between the two blocks

    \resumeSubheading{Hexaware Technologies Pvt Ltd, Pune}{ 13 Sept 2021 \textendash{} 22 Nov 2024}
        {Senior Technical Analyst }{Remote}
        \resumeItemListStart{}
            \item[] \textbf{Project 1:AXA - Belgium}
            \begin{itemize}[leftmargin=0.5in, label={\textbullet}]
                \item As a DevOps engineer in Software Delivery Automation team contributed individually in SDLC process.
                \item Created and maintaned CI/CD pipelines jenkins, Azure DevOps and AWS codebuild based on the applications category compliance.
                \item In Jenkins used scripted as well declarative pipelines using shared libraries where as in azure devops used YAML and template
                 based pipeline.
                \item For automated deployment process a/c multi-environment , setup and configured github,Jenkins and Octopus deploy. Furthermore 
                in Octopus deploy wrote custom-template using bash-shell and  Python.
                \item Apart from the deployment  automate routine operational tasks such as database maintenance, backups, and infrastructure provisioning.
                \item For  Automated infrastructure provisioning used cloud specific Terraform and  Ansible as per stackholders requirement.
                \item Managed containerized applications using Docker and Kubernetes for efficient deployment and scaling.
                \item Implemented auto-scaling and high availability strategies for cloud-native applications also Managed secure cloud networking 
                (VPCs, firewalls, load balancers, VPNs)
                \item Created Python scripts to automate the process of backup and tagging the archived sonarqube projects also using sonarqube Apis.
                Also developed and enhanced several scripts for routine operational tasks.
                \item As a Security & Compliance managed secrets and credentials securely using HashiCorp Vault/AWS Secrets Manager/Azure Key Vault,
                conducted vulnerability scanning with enforced DevSecOps practices within CI/CD pipelines. Also implemented role-based access control (RBAC)
                 and audit trails to ensure security compliance.
                 \item In several applications, implemented and maintained pipelines on AWS using CodePipeline, CodeBuild and CodeDeploy.
                 \item For promoting the application version to higher environment configured dititalAI tool.
                 \item Performed mass migration of artificatories from Nexus to JFrog Artifactory using OS tools.
                 


            \end{itemize}
        \resumeItemListEnd{}
        

        \vspace{10pt} % Space between the two blocks

        \resumeSubheading{Creative Virtual Pvt Ltd, New Mumbai}{03 May 2021 \textendash{} 18 August 2021}
            {Software Engineer}{Remote}
            \resumeItemListStart{}
                \item[] \textbf{Project 1: Admin panel}
                \begin{itemize}[leftmargin=0.5in, label={\textbullet}]
                    \item Design the backend database, develope the API’s and perform the Unit
                    testing.
                    \item Develop the frontend using Angular Framework.
                    \item Deploying the web application to cloud environment.
                    \item Publishing the Docker Image of web application for client
                \end{itemize}
            \resumeItemListEnd{}
    
            \vspace{10pt} % Space between the two blocks

            \resumeSubheading{Terse Software Pvt Ltd, Pune}{14 Feb 2018 \textendash{} 30 April 2021}
                { Software Engineer}{On site}
                \resumeItemListStart{}
                    \item[] \textbf{Project 1: Turtlebean & NPTI}
                    \begin{itemize}[leftmargin=0.5in, label={\textbullet}]
                        \item Responsible development of web as well as mobile application.
                        \item Design and development of web as well as mobile application.
                        \item Collaborate with stakeholders to refine the requirements.
                        \item Provide e2e support and maintanance.
                    \end{itemize}
                \resumeItemListEnd{}
        
   
    
   
\vspace{-17pt}

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart{}
    \resumeProjectHeading{\textbf{Food Mess app} $|$ GitHub Repository: \underline{\url{https://github.com/shubham1507/FoodApp}}}{}
    \vspace{10pt}
        \resumeItemListStart{}
            \resumeItem{Designed, developed the backend Apis using Django REST.}
        \resumeItemListEnd{}
\resumeSubHeadingListEnd{}

\vspace{-17pt}

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart{}
    \resumeSubheading{MGM's \textendash{} College of Engineering}{Nanded, Maharashtra}
        {\textbf{Bachelor of Engineering in Computer Science}}{August 2013 \textendash{} July 2016}
\resumeSubHeadingListEnd{}

% ---------------------------------------------
\end{document}
